Artin Group Presentations Arising from Cluster Algebras

### 2014-07-30 Paper.tex
edits to section 6 and fixed typos in section 4

In our paper, we define $A_{\Gamma}$ to be the Artin group presentation arising from a cluster algebra, where $\Gamma$ is the diagram associated to the cluster algebra. We provide the necessary relations for the generators of the group, and show that these relations hold under mutations of chordless cycles in a diagram. Our main result is to show that this Artin group presentation is invariant up to isomorphism under the mutation equivalence relation. We state the result here, but present the detailed proof in Section \ref{sec:proof_of_main}.

@@

\indent Section \ref{sec:main_definitions} provides the necessary definitions and fundamental results from \cite{BM13} to motivate our own results. For further definitions and references on the topic, we refer the reader to \cite{FZ02}. Section \ref{sec:finite-type_diagrams}  will review theory from \cite{FZ02}, \cite{FZ03} as well as review the classifications (from \cite{BM13}) of mutations of diagrams and their oriented chordless cycles. In Section \ref{sec:defn_artingroup}, we define the appropriate relations for our Artin group presentations. Section \ref{sec:one_relation} specifies how certain relations in chordless cycles imply other relations in those chordless cycles. Finally, Section \ref{sec:proof_of_main} will provide the proof that the Artin group defined for a diagram $\Gamma$ is invariant up to isomorphism under mutations of $\Gamma$. \\

@@

A \textit{cluster algebra} is an integral domain which can be generated by a set of elements called \textit{cluster variables} that satisfy certain exchange relations. Following the style of \cite{FZ02} and \cite{BM13}, we will define cluster algebras in terms of \textit{skew-symmetrisable} matrices (that is, a matrix $B$ such that there exists a diagonal matrix $D$ of the same size with $D_{ii} >0$ such that $DB$ is skew-symmetric). Let $\mathbb{F} = \mathbb{Q}(u_1, u_2, \ldots, u_n)$ be the field of rational functions in $n$ indeterminates over $\mathbb{Q}$. We will define an \textit{intial seed} for the cluster algebra to be a fixed pair $(\textbf{x}, B)$, where $\textbf{x} = \{x_1, \ldots, x_n\}$ is a free generating set of $\mathbb{F}$ and $B$ is an $n \times n$ skew-symmetric matrix. Define $x_k^{\prime} \in \mathbb{F}$ by the \textit{exchange relation}
\begin{displaymath}
x_k^{\prime}x_k = \prod_{B_{ik} > 0}{x_i^{B_{ik}}} + \prod_{B_{ik} < 0}{x_i^{-B_{ik}}}
\end{displaymath}
Then, given an initial seed $(\textbf{x}, B)$ and $k \in {1,2,\ldots,n}$, we can define a \textit{mutation} of the seed at $k$, denoted $\mu_k(\boldsymbol{x}, B) = (\textbf{x}^{\prime}, B^{\prime})$ where:
\begin{displaymath}
B_{ij}^{\prime} = \begin{cases} - B_{ij} & \mbox{ if } i = k \mbox{ or } j = k;\\
																B_{ij} + \frac{|B_{ik}|B_{kj} + B_{ik}|B_{kj}|}{2} & \mbox{ otherwise. }\\
									\end{cases}
\end{displaymath}
and $\textbf{x}^{\prime} = \left{ x_1, x_2, \ldots, x_{k-1}, x_k^{\prime}, x_{k+1}, \ldots, x_n \right}$. 
Such a mutation or a sequence of such mutations generate \textit{seeds} which in turn generate all cluster variables in that, for each $\textbf{x} = \left{ x_1, \ldots, x_n \right}$ corresponding to a seed of the cluster algebra, the entries $x_i$ are the cluster variables. \\

 A cluster algebra is said to be of \textit{finite type} if the number of cluster variables that generate it is finite (if it has finitely many seeds). For each finite type cluster algebra, we can associate to its corresponding skew-symmetrisable matrix an edge-weighted, oriented graph, called a \textit{diagram}. We will often denote this diagram by $\Gamma$, and the vertex set of $\Gamma$ by $\V$. We will denote two connected vertices by $i \rightarrow j$, or by $i\--\ j$ if the orientation is not specified. The diagram is determined by, for $i, j \in \V$, $i \xrightarrow{w} j$ if and only if $B_{ij} > 0$ and $w = |B_{ij}B_{ji}|$ is the weight of the edge. A skew-symmetrisable matrix $B$ is \textit{2-finite} if $|B_{ij}B_{ji}| \leq 3$ for $i, j \in \left{ 1, \ldots, n \right}$.  By \cite[7.5]{FZ02}, we have that if $B$ is 2-finite, all 3-cycles in the unoriented graph underlying our diagram must be oriented cyclically. \\

@@

The rest of the paper will be devoted to building up analogous relations, defined in ~\ref{grp def} to prove a similar result in the case of Artin groups. For $\Gamma$ a diagram of finite type, we define the Artin group associated to $\Gamma$ as in Section \ref{sec:defn_artingroup}. We will then use the group relations presented in this definition to prove the mutation invariance of $A_{\Gamma}$ in Section \ref{sec:proof_of_main}.

@@

    \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
  {
    & |[name = ul]|\circ& |[name = ur]|\bullet\\
    %
    &|[name=dl]| \circ &|[name=dr]| \circ \\
  };
\draw[->]
  (ul) to node[above] {1} (ur)
  ;
  \draw[->]
  (dl) to node[left]{2}(ul)
  ;
  \draw[->]
  (dr) to node[below]{1}(dl)
  ;
  \draw[->]
  (ur) to node[right]{2} (dr)
  ;
    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){k};
   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){k=2};
    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};

@@

\begin{note}
Let 
\begin{align*}
	\langle x_i,x_j \rangle ^k = \begin{cases}
	(x_ix_j)^{\frac{k}{2}}, &\text{ if }k \equiv 0 \pmod 2\\
	(x_ix_j)^{\frac{k-1}{2}}x_i &\text{ if } k \equiv 1 \pmod 2
\end{cases}
\end{align*}
That is, $\langle x_i,x_j \rangle$ is just an alternating sequence of $x_i$ and $x_j$ of length $k.$

@@

\section{Proof of Main Result}\label{sec:proof_of_main}

\noindent In this section we prove our main result:

@@

Throughout this section we will fix a diagram of finite type $\Gamma$, a vertex $k$ of $\Gamma$, and write $\Gamma^{\prime} = \mu_k(\Gamma)$.  We will write $s_i$, $r_i$, $q_i$, and $u_i$ for the generators corresponding to vertex $i$ of $A_{\Gamma}$, $A_{\Gamma^\prime}$, $A_{\Gamma^{op}}$, and $A_{\left(\Gamma^\prime\right)^{op}}$, respectively.  We will also abuse notation and write $u_i$ for the generators of $A_{\left(\Gamma^{op}\right)^\prime}$ as well, making use of the fact that $\left(\Gamma^\prime\right)^{op} = \left(\Gamma^{op}\right)^\prime$.

In the proof of Theorem \ref{thm:main} we will use Lemma \ref{lem:op_homomorphism} along with the following proposition, whose proof we will defer until after the proof of Theorem \ref{thm:main} and then split into Lemmas \ref{lem:r2a_relations}, \ref{lem:r2b_relations}, and \ref{lem:r3_relations}.

@@

@@

\begin{proof}[Proof of Theorem \ref{thm:main}]
By Proposition \ref{prop:ti_relations} $\varphi\colon A_{\Gamma^\prime}\rightarrow A_\Gamma$ is a group homomorphism.  We also abuse notation and write $\varphi\colon A_{\Gamma^{op}}\rightarrow A_{\left(\Gamma^{op}\right)^\prime}$ by letting $\varphi(q_i)$ equal $u_ku_iu_k^{-1}$ if there is an arrow $i\rightarrow k$ in $\left(\Gamma^{op}\right)^\prime$, and $u_i$ otherwise, and this is a homomorphism by Proposition \ref{prop:ti_relations} as well.  By Lemma \ref{lem:op_homomorphism}, the homormorphism $\Delta$ that sends $s_i\in A(\Gamma)$ to $q_i^{-1}\in A(\Gamma^{op})$ and $u_i\in A_{\left(\Gamma^\prime\right)^{op}}$ to $r_i\in A_{\Gamma^\prime}$ is well-defined.  We then have a homomorphism 
$$\psi = \Delta\circ\varphi\circ\Delta\colon A(\Gamma)\rightarrow A(\Gamma^{op})\rightarrow A(\left(\Gamma^{op}\right)^{\prime}) \rightarrow A(\Gamma^{\prime})$$

@@

$$\psi\circ\varphi(r_i) = \Delta(\varphi(\Delta(\varphi(r_i)))) = \Delta(\varphi(\Delta(s_ks_is_k^{-1}))) = \Delta(\varphi(q_k^{-1}q_i^{-1}q_k)) = \Delta(u_i^{-1}) = r_i$$

@@

$$\psi\circ\varphi(r_i) = \Delta(\varphi(\Delta(\varphi(r_i)))) = \Delta(\varphi(\Delta(s_i))) = \Delta(\varphi(q_i^{-1})) = \Delta(u_i^{-1}) = r_i$$

Thus $\psi\circ\varphi$ is the identity map on $A(\Gamma^{\prime})$.  By a similar argument $\varphi\circ\psi$ is the identity map on $A(\Gamma)$, and hence $A(\Gamma)\cong A(\Gamma^{\prime}))$.
\end{proof}

We prove Proposition \ref{prop:ti_relations} by showing that that the elements $\varphi(r_i)\in A_\Gamma$ satisfy the $(R2^\prime)$ and $(R3^\prime)$ relations in $A_{\Gamma^\prime}$.  Proofs that the $t_i$ satisfy these relations are divided among Lemmas \ref{lem:r2a_relations}, \ref{lem:r2b_relations}, and \ref{lem:r3_relations}.  Throughout the proofs we write $t_i = \varphi(r_i)$ for convenience.

\begin{lem}\label{lem:r2a_relations}
Let $i,j$ be distinct vertices of $\Gamma$.
\begin{enumerate}[(a)]
\item If $i=k$ or $j=k$, then $\langle t_it_j \rangle^k = e$.
\item If at most of $i,j$ is connected to $k$ in $\Gamma$, then $\langle t_it_j \rangle^k = e$.
\end{enumerate}
\end{lem}

\begin{proof}
For case $(a)$, suppose without loss of generality that $i=k$.  Note that $m_{ij}^\prime = m_{ij}$. The only nontrivial case is when there is an arrow $j\rightarrow k =i$.  Since $i$ and $j$ are connected in this case, $m_{ij}$ is one of 3,4, or 6.

\vskip.1in
\noindent
{\sf Case $m_{ij} = 3$}.
Here we have $s_js_is_j = s_is_js_i$, so $s_is_j = s_js_is_js_i^{-1}$, so

$$t_it_jt_i = s_is_is_js_i^{-1}s_i = s_is_is_j = s_is_js_is_js_i^{-1} = t_jt_it_j$$

\vskip.1in
\noindent
{\sf Case $m_{ij} = 4$}.  Here we have $s_is_js_is_j = s_js_is_js_i$, so $s_is_is_js_is_js_i^{-1} = s_is_js_is_j$ and therefore

$$t_it_jt_it_j = s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_is_js_is_js_i^{-1} = s_is_js_is_j = s_is_js_i^{-1}s_is_is_js_i^{-1}s_i = t_jt_it_jt_i$$

\vskip.1in
\noindent
{\sf Case $m_{ij} = 6$}.  Here we have $s_is_is_js_is_js_is_js_i^{-1} = s_is_js_is_js_is_j$.  As in the previous case, we add an remove pairs $s_is_i^{-1}$ as necessary, giving

$$t_it_jt_it_jt_it_j = s_is_is_js_i^{-1}s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_js_i^{-1}s_is_is_js_i^{-1}s_is_is_js_i^{-1}s_i = t_jt_it_jt_it_jt_i$$

@@

\vskip.1in
\noindent
{\sf Case $m_{ij} = 2$}.  Here $s_is_j = s_js_i$, so we have that

@@

\vskip.1in
\noindent
{\sf Case $m_{ij} = 3$}.  Here $s_is_js_i = s_js_is_j$, so we have that

$$t_it_jt_i = s_ks_is_k^{-1}s_js_ks_is_k^{-1} = s_ks_is_js_is_k^{-1} = s_ks_js_is_js_k^{-1} = s_js_ks_is_k^{-1}s_j = t_jt_it_j$$

\vskip.1in
\noindent
{\sf Case $m_{ij} = 4$}.  Here $s_is_js_is_j = s_js_is_js_i$, so we have that

$$t_it_jt_it_j = s_ks_is_k^{-1}s_js_ks_is_k^{-1}s_j = s_ks_is_js_is_js_k^{-1} = s_ks_js_is_js_is_k^{-1} = s_js_ks_is_k^{-1}s_js_ks_is_k^{-1} = t_jt_it_jt_i$$

\vskip.1in
\noindent
{\sf Case $m_{ij} = 6$}.  Here $s_is_js_is_js_is_j = s_js_is_js_is_js_i$, so we have that

$$t_it_jt_it_jt_it_j = s_ks_is_k^{-1}s_js_ks_is_k^{-1}s_js_ks_is_k^{-1}s_j = s_ks_is_js_is_js_is_js_k^{-1} = s_ks_js_is_js_is_js_is_k^{-1} = t_jt_it_jt_it_jt_i$$

\end{proof}

\begin{lem}\label{lem:r2b_relations}
Let $i,j$ be distinct vertices of $\Gamma$ such that $i$ and $j$ are connected.  Then $\langle t_it_j \rangle^k = e$.
\end{lem}

\begin{proof}
The possibilities for the subdiagram induced by $i$, $j$, and $k$ are enumerated in Corollary \ref{local_three_picture}.  We show that $t_i$ and $t_j$ satisfy the $(R2^\prime)$ relations by checking each case.  We also check that the corresponding $(R3^\prime)$ relations hold in cases (b), (d), (e), and (f).  Within each case we view the subdiagram on the left as a subdiagram of $\Gamma$ in the subcase $(i)$ and as a subdiagram of $\Gamma^\prime$ in the subcase $(ii)$.\todo{Disaster.  Open to suggestions for how to make this more clear}

@@

\begin{enumerate}[a)]
\item
\begin{enumerate}[i)]
\item We have $t_it_j = s_ks_is_k^{-1}s_ks_js_k^{-1} = s_ks_is_js_k^{-1} = s_ks_js_is_k^{-1} = t_jt_i$.
\item We have $t_it_j = s_is_j = s_js_i = t_jt_i$.
\end{enumerate}
\item
\begin{enumerate}[i)]
\item We have
\begin{align*}
t_it_jt_i &= s_ks_i\underline{s_k^{-1}s_js_k}s_is_k^{-1}\\
&= s_k\underline{s_is_j}s_k\underline{s_j^{-1}s_i}s_k^{-1}\\
&= s_ks_j\underline{s_is_ks_i}s_j^{-1}s_k^{-1}\\
&= \underline{s_ks_js_k}s_i\underline{s_ks_j^{-1}s_k^{-1}}\\
&= s_js_k\underline{s_js_is_j^{-1}}s_k^{-1}s_j\\
&= s_js_ks_is_k^{-1}s_j\\
&= t_it_jt_i
\end{align*}

\item We have $t_it_j = s_i\underline{s_ks_js_k^{-1}} = \underline{s_is_j^{-1}s_ks_j} = \underline{s_j^{-1}s_ks_j}s_i = s_ks_js_k^{-1}s_i = t_jt_i$
\end{enumerate}
\item
\begin{enumerate}[i)]
\item We have $t_it_j = s_ks_is_k^{-1}s_ks_js_k^{-1} = s_ks_is_js_k^{-1} = s_ks_js_is_k^{-1} = t_jt_i$
\item We have $t_it_j = s_is_j = s_js_i = t_jt_i$
\end{enumerate}
\item
\begin{enumerate}[i)]
\item We have
\begin{align*}
t_it_jt_it_jt_i^{-1}t_j^{-1}t_i^{-1}t_j^{-1} &= s_ks_is_k^{-1}s_js_ks_i\underline{s_k^{-1}s_js_k}s_i^{-1}\underline{s_k^{-1}s_j^{-1}s_k}s_i^{-1}s_k^{-1}s_j^{-1}\\
&=s_ks_is_k^{-1}\underline{s_js_ks_is_j}s_k\underline{s_j^{-1}s_i^{-1}s_j}s_k^{-1}s_j^{-1}s_i^{-1}s_k^{-1}s_j^{-1}\\
&=s_k\underline{s_is_k^{-1}s_ks_j}s_ks_is_ks_i^{-1}s_k^{-1}\underline{s_j^{-1}s_i^{-1}s_k^{-1}s_j^{-1}}\\
&=s_ks_j\underline{s_is_ks_is_ks_i^{-1}s_k^{-1}s_i^{-1}s_k^{-1}}s_j^{-1}s_k^{-1}\\
&= e
\end{align*}

>>>>

In our paper, we define $A_{\Gamma}$ to be the Artin group presentation arising from a cluster algebra, where $\Gamma$ is the diagram associated to the cluster algebra. We provide the necessary relations for the generators of the group, and show that these relations hold under mutations of chordless cycles in a diagram. Our main result is to show that this Artin group presentation is invariant up to isomorphism under the mutation equivalence relation. We state the result here, but present the detailed proof in Section \ref{sec:main_result}.

@@

\indent Section \ref{sec:main_definitions} provides the necessary definitions and fundamental results from \cite{BM13} to motivate our own results. For further definitions and references on the topic, we refer the reader to \cite{FZ02}. Section \ref{sec:finite-type_diagrams}  will review theory from \cite{FZ02}, \cite{FZ03} as well as review the classifications (from \cite{BM13}) of mutations of diagrams and their oriented chordless cycles. In Section \ref{sec:defn_artingroup}, we define the appropriate relations for our Artin group presentations. Section \ref{sec:one_relation} specifies how certain relations in chordless cycles imply other relations in those chordless cycles. Finally, Section \ref{sec:main_result} will provide the proof that the Artin group defined for a diagram $\Gamma$ is invariant up to isomorphism under mutations of $\Gamma$. \\

@@

A \textit{cluster algebra} is an integral domain which can be generated by a set of elements called \textit{cluster variables} that satisfy certain exchange relations. Following the style of \cite{FZ02} and \cite{BM13}, we will define cluster algebras in terms of \textit{skew-symmetrisable} matrices (that is, a matrix $B$ such that there exists a diagonal matrix $D$ of the same size with $D_{ii} >0$ such that $DB$ is skew-symmetric). Let $\mathbb{F} = \mathbb{Q}(u_1, u_2, \ldots, u_n)$ be the field of rational functions in $n$ indeterminates over $\mathbb{Q}$. We will define an \textit{intial seed} for the cluster algebra to be a fixed pair $(\textbf{x}, B)$, where $\textbf{x} = \{x_1, \ldots, x_n\}$ is a free generating set of $\mathbb{F}$ and $B$ is an $n \times n$ skew-symmetric matrix. Define $x_k^{\prime} \in \mathbb{F}$ by the \textit{exchange relation}
\begin{displaymath}
x_k^{\prime}x_k = \prod_{B_{ik} > 0}{x_i^{B_{ik}}} + \prod_{B_{ik} < 0}{x_i^{-B_{ik}}}
\end{displaymath}
Then, given an initial seed $(\textbf{x}, B)$ and $k \in {1,2,\ldots,n}$, we can define a \textit{mutation} of the seed at $k$, denoted $\mu_k(\boldsymbol{x}, B) = (\textbf{x}^{\prime}, B^{\prime})$ where:
\begin{displaymath}
B_{ij}^{\prime} = \begin{cases} - B_{ij} & \mbox{ if } i = k \mbox{ or } j = k;\\
																B_{ij} + \frac{|B_{ik}|B_{kj} + B_{ik}|B_{kj}|}{2} & \mbox{ otherwise. }\\
									\end{cases}
\end{displaymath}
and $\textbf{x}^{\prime} = { x_1, x_2, \ldots, x_{k-1}, x_k^{\prime}, x_{k+1}, \ldots, x_n}$. 
Such a mutation or a sequence of such mutations generate \textit{seeds} which in turn generate all cluster variables in that, for each $\textbf{x} = { x_1, \ldots, x_n}$ corresponding to a seed of the cluster algebra, the entries $x_i$ are the cluster variables. \\

 A cluster algebra is said to be of \textit{finite type} if the number of cluster variables that generate it is finite (if it has finitely many seeds). For each finite type cluster algebra, we can associate to its corresponding skew-symmetrisable matrix an edge-weighted, oriented graph, called a \textit{diagram}. We will often denote this diagram by $\Gamma$, and the vertex set of $\Gamma$ by $\V$. We will denote two connected vertices by $i \rightarrow j$, or by $i\--\ j$ if the orientation is not specified. The diagram is determined by, for $i, j \in \V$, $i \xrightarrow{w} j$ if and only if $B_{ij} > 0$ and $w = |B_{ij}B_{ji}|$ is the weight of the edge. A skew-symmetrisable matrix $B$ is \textit{2-finite} if $|B_{ij}B_{ji}| \leq 3$ for $i, j \in { 1, \ldots, n }$.  By \cite[7.5]{FZ02}, we have that if $B$ is 2-finite, all 3-cycles in the unoriented graph underlying our diagram must be oriented cyclically. \\

@@

The rest of the paper will be devoted to building up analogous relations, defined in ~\ref{grp def} to prove a similar result in the case of Artin groups. For $\Gamma$ a diagram of finite type, we define the Artin group associated to $\Gamma$ as in Section \ref{sec:defn_artingroup}. We will then use the group relations presented in this definition to prove the mutation invariance of $A_{\Gamma}$ in Section \ref{sec:main_result}.

@@

    \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
  {
    & |[name = ul]|\circ& |[name = ur]|\bullet\\
    %
    &|[name=dl]| \circ &|[name=dr]| \circ \\
  };
\draw[->]
  (ul) to node[above] {1} (ur)
  ;
  \draw[->]
  (dl) to node[left]{2}(ul)
  ;
  \draw[->]
  (dr) to node[below]{1}(dl)
  ;
  \draw[->]
  (ur) to node[right]{2} (dr)
  ;
    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){1};
   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){k=2};
    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};

@@

\begin{note}
Let 
\begin{align*}
	\langle x_i,x_j \rangle ^k = \begin{cases}
	(x_ix_j)^{\frac{k}{2}}, &\text{ if }k \equiv 0 \pmod 2\\
	(x_ix_j)^{\frac{k-1}{2}}x_i &\text{ if } k \equiv 1 \pmod 2
\end{cases}
\end{align*}
That is, $\langle x_i,x_j \rangle$ is just an alternating sequence of $x_i$ and $x_j$ of length $k$.  We also write $\langle x_i,x_j\rangle^{-k}$ to denote $\left(\langle x_i,x_j\rangle^k\right)^{-1}$

@@

\section{Main Result}\label{sec:main_result}
\noindent In Section \ref{sec:proof_of_main_result} we prove our main result:

@@

Throughout the section we will fix a diagram of finite type $\Gamma$, a vertex $k$ of $\Gamma$, and write $\Gamma^{\prime} = \mu_k(\Gamma)$.  We will write $s_i$, $r_i$, $q_i$, and $u_i$ for the generators corresponding to vertex $i$ of $A_{\Gamma}$, $A_{\Gamma^\prime}$, $A_{\Gamma^{op}}$, and $A_{\left(\Gamma^\prime\right)^{op}}$, respectively. Note that the $u_i$ are generators $A_{\left(\Gamma^{op}\right)^\prime}$ as well, since $\left(\Gamma^\prime\right)^{op} = \left(\Gamma^{op}\right)^\prime$.  In the proof of Theorem \ref{thm:main} we will use Lemma \ref{lem:op_homomorphism} along with the following proposition, which we prove in Section \ref{sec:proof_of_ti_relations}.

@@

\subsection{Proof of Main Result}\label{sec:proof_of_main_result}

@@

\begin{proof}[Proof of Theorem \ref{thm:main}]
By Proposition \ref{prop:ti_relations} $\varphi\colon A_{\Gamma^\prime}\rightarrow A_\Gamma$ is a group homomorphism and $\varphi_{op}\colon A_{\Gamma^{op}}\rightarrow A_{\left(\Gamma^{op}\right)^\prime}$ defined by

\begin{displaymath}
\varphi_{op}(q_i) = \begin{cases}    u_ku_iu_k^{-1} & \mbox{if there is a (possibly weighted) arrow } i \rightarrow k \mbox{ in } \left(\Gamma^{op}\right)^\prime\\
				u_i & \mbox{otherwise}\\
	\end{cases}
\end{displaymath}

\noindent is a group homomorphism as well.  By Lemma \ref{lem:op_homomorphism}, there exist two well-defined homomorphisms $\Delta\colon A_{\Gamma}\rightarrow A_\Gamma^{op}$ defined by $\Delta(s_i) = q_i^{-1}$ and $\Delta^\prime\colon A_{\left(\Gamma^\prime\right)^{op}} \rightarrow A_{\Gamma^\prime}$ defined by $\Delta^\prime(u_i) = r_i^{-1}$. We then have a homomorphism

$$\psi = \Delta^\prime\circ\varphi_{op}\circ\Delta\colon A(\Gamma)\rightarrow A(\Gamma^{op})\rightarrow A(\left(\Gamma^{op}\right)^{\prime}) \rightarrow A(\Gamma^{\prime})$$

@@

$$\psi\circ\varphi(r_i) = \Delta^\prime(\varphi_{op}(\Delta(\varphi(r_i)))) = \Delta^\prime(\varphi_{op}(\Delta(s_ks_is_k^{-1}))) = \Delta^\prime(\varphi_{op}(q_k^{-1}q_i^{-1}q_k)) = \Delta^\prime(u_i^{-1}) = r_i$$

@@

$$\psi\circ\varphi(r_i) = \Delta^\prime(\varphi_{op}(\Delta(\varphi(r_i)))) = \Delta^\prime(\varphi_{op}(\Delta(s_i))) = \Delta^\prime(\varphi_{op}(q_i^{-1})) = \Delta^\prime(u_i^{-1}) = r_i$$

Thus $\psi\circ\varphi$ is the identity map on $A_{\Gamma^{\prime}}$.  By a similar argument $\varphi\circ\psi$ is the identity map on $A_\Gamma$, and hence $A_\Gamma\cong A_{\Gamma^{\prime}}$.
\end{proof}

\subsection{Proof of Proposition \ref{prop:ti_relations}}\label{sec:proof_of_ti_relations}

We prove Proposition \ref{prop:ti_relations} by showing that that the elements $\varphi(r_i)\in A_\Gamma$ satisfy the $(R2^\prime)$ and $(R3^\prime)$ relations in $A_{\Gamma^\prime}$.  The proof that the $\varphi(r_i)$ satisfy these relations is divided among Lemmas \ref{lem:r2a_relations}, \ref{lem:r2b_relations}, and \ref{lem:r3_relations}.  Throughout the proofs we write $t_i = \varphi(r_i)$ for convenience.

\begin{lem}\label{lem:r2a_relations}
Let $i,j$ be distinct vertices of $\Gamma$.
\begin{enumerate}[(a)]
\item If $i=k$ or $j=k$, then $\langle t_it_j \rangle^{m_{ij}^\prime} = \langle t_jt_i \rangle^{m_{ij}^\prime}$.
\item If at most one of $i,j$ is connected to $k$ in $\Gamma$, then $\langle t_it_j \rangle^{m_{ij}^\prime} = \langle t_jt_i \rangle^{m_{ij}^\prime}$.
\end{enumerate}
\end{lem}

\begin{proof}
For case $(a)$, suppose without loss of generality that $i=k$.  Note that $m_{ij}^\prime = m_{ij}$. The only nontrivial case is when there is an arrow $j\rightarrow k =i$.  Since $i$ and $j$ are connected in this case, $m_{ij}$ is one of 3, 4, or 6.

\vskip.1in
\noindent
{\sf Case $m_{ij} = 3$}.
Here $\langle s_js_i \rangle^{3} = \langle s_is_j \rangle^{3}$, so $s_is_j = s_js_is_js_i^{-1}$ and we have

$$\langle t_it_j \rangle^{3} = t_it_jt_i = s_is_is_js_i^{-1}s_i = s_is_is_j = s_is_js_is_js_i^{-1} = t_jt_it_j = \langle t_jt_i \rangle^{3}$$

\vskip.1in
\noindent
{\sf Case $m_{ij} = 4$}.  Here $\langle s_is_j \rangle^{4} = \langle s_js_i \rangle^{4}$, so $s_is_is_js_is_js_i^{-1} = s_is_js_is_j$ and therefore

$$\langle t_it_j \rangle^{4} = s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_is_js_is_js_i^{-1} = s_is_js_is_j = s_is_js_i^{-1}s_is_is_js_i^{-1}s_i = \langle t_jt_i \rangle^{4}$$

\vskip.1in
\noindent
{\sf Case $m_{ij} = 6$}.  Here $\langle s_is_j \rangle^{6} = \langle s_js_i \rangle^{6}$, so $s_is_is_js_is_js_is_js_i^{-1} = s_is_js_is_js_is_j$.  As in the previous case, we add and remove pairs $s_is_i^{-1}$ as necessary, giving

$$\langle t_it_j \rangle^{6} = s_is_is_js_i^{-1}s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_js_i^{-1}s_is_is_js_i^{-1}s_is_is_js_i^{-1}s_i = \langle t_it_j \rangle^{6}$$

@@

\vskip.1in
\noindent
{\sf Case $m_{ij} = 2$}.  Here $s_is_j = s_js_i$, so $s_j$ commutes with both $s_i$ and $s_k$ and we have that

@@

\vskip.1in
\noindent
{\sf Case $m_{ij} = 3$}.  Here $\langle s_is_j \rangle^{3} = \langle s_js_i \rangle^{3}$, so we have that

$$\langle t_it_j \rangle^{3} = s_ks_is_k^{-1}s_js_ks_is_k^{-1} = s_ks_is_js_is_k^{-1} = s_ks_js_is_js_k^{-1} = s_js_ks_is_k^{-1}s_j = \langle t_jt_i \rangle^{3}$$

\vskip.1in
\noindent
{\sf Case $m_{ij} = 4$}.  Here $\langle s_is_j \rangle^{4} = \langle s_js_i \rangle^{4}$, so we have that

$$\langle t_it_j \rangle^{4} = s_ks_is_k^{-1}s_js_ks_is_k^{-1}s_j = s_ks_is_js_is_js_k^{-1} = s_ks_js_is_js_is_k^{-1} = s_js_ks_is_k^{-1}s_js_ks_is_k^{-1} = \langle t_jt_i \rangle^{4}$$

\vskip.1in
\noindent
{\sf Case $m_{ij} = 6$}.  Here $\langle s_is_j \rangle^{6} = \langle s_js_i \rangle^{6}$, so we have that

$$\langle t_it_j \rangle^{6} = s_ks_is_k^{-1}s_js_ks_is_k^{-1}s_js_ks_is_k^{-1}s_j = s_ks_is_js_is_js_is_js_k^{-1} = s_ks_js_is_js_is_js_is_k^{-1} = \langle t_it_j \rangle^{6}$$
\end{proof}

\begin{lem}\label{lem:r2b_relations}
Let $i,j$ be distinct vertices of $\Gamma$ such that $i$ and $j$ are connected.  Then $\langle t_it_j \rangle^{m_{ij}^\prime} = \langle t_jt_i \rangle^{m_{ij}^\prime}$.
\end{lem}

\begin{proof}
The possibilities for the subdiagram induced by $i$, $j$, and $k$ are enumerated in Corollary \ref{local_three_picture}.  We show that $t_i$ and $t_j$ satisfy the $(R2^\prime)$ relations by checking each case.  Within each case, subcase $(i)$ is when the subdiagram of $\Gamma$ is the diagram on the left in the figure in Corollary \ref{local_three_picture}, and subcase $(ii)$ is when the subdiagram of $\Gamma$ is the diagram on the right in the figure in Corollary \ref{local_three_picture}.

@@

\begin{enumerate}[a)]
\item
\begin{enumerate}[i)]
\item We have $\langle t_it_j \rangle^{2} = s_ks_is_k^{-1}s_ks_js_k^{-1} = s_ks_is_js_k^{-1} = s_ks_js_is_k^{-1} = \langle t_jt_i \rangle^{2}$.
\item We have $\langle t_it_j \rangle^{2} = s_is_j = s_js_i = \langle t_jt_i \rangle^{2}$.
\end{enumerate}
\item
\begin{enumerate}[i)]
\item We have
\begin{align*}
\langle t_it_j \rangle^{3} &= s_ks_i\underline{s_k^{-1}s_js_k}s_is_k^{-1}\\
&= s_k\underline{s_is_j}s_k\underline{s_j^{-1}s_i}s_k^{-1}\\
&= s_ks_j\underline{s_is_ks_i}s_j^{-1}s_k^{-1}\\
&= \underline{s_ks_js_k}s_i\underline{s_ks_j^{-1}s_k^{-1}}\\
&= s_js_k\underline{s_js_is_j^{-1}}s_k^{-1}s_j\\
&= s_js_ks_is_k^{-1}s_j\\
&= \langle t_jt_i \rangle^{3}
\end{align*}

\item We have $\langle t_it_j \rangle^{2} = s_i\underline{s_ks_js_k^{-1}} = \underline{s_is_j^{-1}s_ks_j} = \underline{s_j^{-1}s_ks_j}s_i = s_ks_js_k^{-1}s_i = \langle t_jt_i \rangle^{2}$
\end{enumerate}
\item
\begin{enumerate}[i)]
\item We have $\langle t_it_j \rangle^{2} = s_ks_is_k^{-1}s_ks_js_k^{-1} = s_ks_is_js_k^{-1} = s_ks_js_is_k^{-1} = \langle t_jt_i \rangle^{2}$
\item We have $\langle t_it_j \rangle^{2} = s_is_j = s_js_i = \langle t_jt_i \rangle^{2}$
\end{enumerate}
\item
\begin{enumerate}[i)]
\item We have
\begin{align*}
\langle t_it_j \rangle^{4}\langle t_jt_i \rangle^{-4} &= t_it_jt_it_jt_i^{-1}t_j^{-1}t_i^{-1}t_j^{-1}\\
 &= s_ks_is_k^{-1}s_js_ks_i\underline{s_k^{-1}s_js_k}s_i^{-1}\underline{s_k^{-1}s_j^{-1}s_k}s_i^{-1}s_k^{-1}s_j^{-1}\\
&=s_ks_is_k^{-1}\underline{s_js_ks_is_j}s_k\underline{s_j^{-1}s_i^{-1}s_j}s_k^{-1}s_j^{-1}s_i^{-1}s_k^{-1}s_j^{-1}\\
&=s_k\underline{s_is_k^{-1}s_ks_j}s_ks_is_ks_i^{-1}s_k^{-1}\underline{s_j^{-1}s_i^{-1}s_k^{-1}s_j^{-1}}\\
&=s_ks_j\underline{s_is_ks_is_ks_i^{-1}s_k^{-1}s_i^{-1}s_k^{-1}}s_j^{-1}s_k^{-1}\\
&= s_ks_j\langle s_is_j \rangle^{4}\langle s_js_i \rangle^{-4}s_j^{-1}s_k^{-1} \\
&= e
\end{align*}
